The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-23 paper/ms.tex
working on the results section

This paper is structured as follows: In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. We also list the different physical parameters in
the simulated grid of models. In the next \S \ref{sec:results} we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the sphere
rotational velocity. In \S \ref{sec:discussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modeling of the \ly line. In the last section we present
our conclusions.

In this paper we express a photon's frequency in terms of the
dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_\alpha$, where
$\nu_{\alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
frequency,  $\Delta\nu_{\alpha} \equiv
\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the Doppler
broadening of the line which depends on the neutral gas temperature
$T$ scattering the radiation or equivalently the thermal velocity
$v_{\rm th}$ of the atoms.

@@

The first quantitative conclusion of the effect of rotation in the
\ly line is that double peaks broaden and reduce their intensity
while the line center rises. This gives the impression that, as the
rotational velocity increases, the double peaks are merged into a
single broad emission peak. This is most evident at the highest
rotational velocities for the homogeneously distributed sources
(right panel in Figure \ref{fig:differentvelocities}).

To quantify the line broadening we use the width at half maximum
(FWHM), $W_{1/2}$. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
with rotational velocity. Continuous (dashed) lines connect the
results for homogeneous (central) source distribution. For the
temperature $T=10^4$K used in our radiative transfer calculations the
thermal velocity is $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it
means that the FWHM increase up to $350$\kms (at $V_{\rm
  max}=300$\kms) compared to $150$\kms in the static case.

% No entiendo bien esta ultima frase, la comparasion es entre que modelos? con que \tau_H?. Nicolas

>>>>

This paper is structured as follows: In \S \ref{sec:implementation} we
present the implementation of bulk rotation into the Monte Carlo
codes, paying special attention to coordinate definitions. We also
present a short review of how the \ly radiative transfer codes work
and list the different physical parameters in the simulated grid of
models. In the next \S \ref{sec:results} we present the results of the
simulations, with special detail to quantities in the line that show a
clear evolution as a function of the sphere rotational velocity. In \S
\ref{sec:discussion} we discuss the implications of our results in the
interpretation of LAEs observations. In the last section we present
our conclusions.

In this paper we express a photon's frequency in terms of the
dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_\alpha$, where
$\nu_{\alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
frequency,  $\Delta\nu_{\alpha} \equiv
\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the Doppler
broadening of the line which depends on the neutral gas temperature
$T$ scattering the radiation or equivalently the thermal velocity
$v_{\rm th}$ of the atoms.  For the temperature $T=10^4$K used in our
radiative transfer calculations the thermal velocity is
$v_{th}=12.8$\kms.

@@

There are three clear effects on the line's morphology as the
rotational veloctiy increases. First, the line
broadens; second, the double peaks reduce their intensity; and third,
the intensity at the line center rises. The two last effects give the
impresion that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in right panel in Figure \ref{fig:differentvelocities}.

We use the full width at half maximum (FWHM), $W_{1/2}$to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
with rotational velocity. {\bf Here we need to check the numbers to
  say something more specific.}

We parameterize the dependency of the linewidth as $W_{1/2}^2 =
W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for the
